---
title: "2019-02-01_Gierzynski_NL_MCI"
author: "Nicolas May"
date: "2/1/2019"
output: 
  html_document:
    theme: cerulean
    highlight: espresso
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Requirements

## Load Useful Libraries

```{r}
library(dplyr)
library(stringr)
```

## Load Useful Variables / Helpers

```{r}
source("~/Desktop/config.R")
rm(BOX_CLIENT_ID); rm(BOX_CLIENT_SECRET); rm(BOX_REDIRECT_URI);
source("~/Desktop/helpers.R")

# switch to access API (TRUE) or not (FALSE)
get_api_data <- TRUE
```

# Get Data

## Define UDS 3 and MiNDSet Data Fields

### UDS 3
```{r}
fields_u3_raw <- 
  c(
    "ptid"
    , "form_date"
    , "mrn"
    , "madc_id"
    , "dob"
    # , "race"
    # , "sex"
    # , "handed"
    # , "educ"
    # , "maristat"
    , "mocatots"
    # , "fu_sex"
    # , "fu_maristat"
    , "fu_mocatots"
  )
fields_u3 <- fields_u3_raw %>% paste(collapse = ",")
```

### MiNDSet Registry
```{r}
fields_ms_raw <- 
  c(
    "subject_id"
    , "exam_date"
    , "race_value" # 1 Wht, 2 Blk, 3 Asn, 4 Hsp, 5 Oth, 6 Unk
    , "sex_value"  # 1 M, 2 F
    , "handedness" # ___1 R, ___2 L, ___3 A
    , "ed_level"
    , "marital_status" # 1 Mrd, 2 Wdw, 3 Dvc, 4 Spt, 5 NvM, 6 Sng, 7 Oth
    , "uds_dx"
    , "reg_num" # mrn
    , "madc_id"
    , "date"    # rvf date
    , "first_name"
    , "last_name"
    , "street"
    , "pt_city"
    , "state"
    , "zip_code"
    , "county"
    , "homephone_number"
    , "work_phone"
    , "cell_phone"
    , "primary_lang" # 1 Eng, 2 Spn, 3 Oth
    , "so_fname"    # S/O name
    , "street_name" # S/O street address
    , "so_city"
    , "so_state"
    , "so_zip"
    , "so_homephone"
    , "so_workphone"
    , "so_cellphone"
    , "so_relationship"
    , "feedback"
    , "fb_complete"
    , "notes_box"
    , "res_refer"
  )
fields_ms <- fields_ms_raw %>% paste(collapse = ",")
```

## Retrieve Data via REDCap API

### UDS 3
```{r}
if (get_api_data) {
  json_u3 <- rc_api_get(token  = REDCAP_API_TOKEN_UDS3n,
                        fields = fields_u3)
  json_u3 <- str_replace_all(json_u3, "\r\n", " ")
}

df_u3 <- jsonlite::fromJSON(json_u3) %>% na_if("")
```

### MiNDSet Registry
```{r}
if (get_api_data) {
  json_ms <- rc_api_get(token  = REDCAP_API_TOKEN_MINDSET,
                        fields = fields_ms)
  json_ms <- str_replace_all(json_ms, "\r\n", " ")
}

df_ms <- jsonlite::fromJSON(json_ms) %>% na_if("")
```

## Write Raw Data to CSV

### UDS 3
```{r}
readr::write_csv(df_u3, "df_u3.csv", na = "")
```

### MiNDSet Registry
```{r}
readr::write_csv(df_ms, "df_ms.csv", na = "")
```


# Process Data

## Clean Data 

### UDS 3

Clean out DDEs.
```{r}
df_u3_cln <- df_u3 %>% 
  filter(str_detect(ptid, "^UM\\d{8}$"))
```

Clean out missing `forms_date`s.
```{r}
df_u3_cln <- df_u3_cln %>% 
  filter(!is.na(form_date))
```

Re-type fields appropriately.
```{r}
# glimpse(df_u3_cln)
# tail(df_u3_cln)
df_u3_cln <- df_u3_cln %>% 
  mutate(form_date = as_date(form_date),
         dob = as_date(dob),
         # sex = as.integer(sex),
         # race = as.integer(race),
         # educ = as.integer(educ),
         # maristat = as.integer(maristat),
         # handed = as.integer(handed),
         mocatots = as.integer(mocatots),
         # fu_maristat = as.integer(fu_maristat),
         # fu_sex = as.integer(fu_sex),
         fu_mocatots = as.integer(fu_mocatots))
```

Collapse IVP / FVP / TVP fields.
```{r}
collapsible_fields <- get_ift_dups(names(df_u3_cln))

df_u3_cln_copy <- df_u3_cln

for (field in collapsible_fields) {
  df_u3_cln_copy <- collapse_ift_cols(df_u3_cln_copy, !!field) # <= NOTICE !!
}

df_u3_cln <- df_u3_cln_copy
rm(df_u3_cln_copy)
```

Propogate demographic data over NAs.
```{r}
# glimpse(df_u3_cln)
# dob
df_u3_cln <- df_u3_cln %>% 
  propagate_value(ptid, form_date, dob)
# # sex
# df_u3_cln <- df_u3_cln %>% 
#   propagate_value(ptid, form_date, sex)
# # race
# df_u3_cln <- df_u3_cln %>% 
#   propagate_value(ptid, form_date, race)
# # educ
# df_u3_cln <- df_u3_cln %>% 
#   propagate_value(ptid, form_date, educ)
# # maristat
# df_u3_cln <- df_u3_cln %>% 
#   propagate_value(ptid, form_date, maristat)
# # handed
# df_u3_cln <- df_u3_cln %>% 
#   propagate_value(ptid, form_date, handed)
```

Calculate age.
```{r}
df_u3_cln <- df_u3_cln %>% 
  calculate_age(dob = dob, visit_date = today()) %>% 
  select(-age_years, -age_units)
```


### MiNDSet Registry

```{r}
# glimpse(df_ms)
# head(df_ms, n = 10)
```

Clean out missing `exam_date`s.
```{r}
df_ms_cln <- df_ms %>% 
  filter(!is.na(exam_date))
```

Clean out non-UMMAP IDs.
```{r}
df_ms_cln <- df_ms_cln %>% 
  filter(str_detect(subject_id, "^UM\\d{8}$"))
```

Re-type fields appropriately.
```{r}
# glimpse(df_ms_cln)
df_ms_cln <- df_ms_cln %>%
  mutate(date = as_date(date),
         race_value = as.integer(race_value),
         sex_value = as.integer(sex_value),
         handedness___1 = as.integer(handedness___1),
         handedness___2 = as.integer(handedness___2),
         handedness___3 = as.integer(handedness___3),
         ed_level = as.integer(ed_level),
         primary_lang = as.integer(primary_lang),
         marital_status = as.integer(marital_status),
         exam_date = as_date(exam_date),
         feedback = as.integer(feedback),
         fb_complete = as.integer(fb_complete))

```

Mutate `handedness___*` fields.
```{r}
df_ms_cln <- df_ms_cln %>% 
  mutate(handedness = case_when(
    handedness___3 == 1 ~ 3L,
    handedness___2 == 1 ~ 2L,
    handedness___1 == 1 ~ 1L
  )) %>% 
  select(-starts_with("handedness___"))
```

Propogate demographic data over NAs.
```{r}
# glimpse(df_ms_cln)
# race_value
df_ms_cln <- df_ms_cln %>% 
  propagate_value(subject_id, exam_date, race_value)
# sex_value
df_ms_cln <- df_ms_cln %>% 
  propagate_value(subject_id, exam_date, race_value)
# ed_level
df_ms_cln <- df_ms_cln %>% 
  propagate_value(subject_id, exam_date, race_value)
# primary_lang
df_ms_cln <- df_ms_cln %>% 
  propagate_value(subject_id, exam_date, race_value)
# handedness
df_ms_cln <- df_ms_cln %>% 
  propagate_value(subject_id, exam_date, race_value)
```


# Join Data

## Left Join: UDS 3 (L) + MiNDSet Registry (R)

```{r}
df_u3_ms <-
  FuzzyDateJoin::outer_left(
    x = df_u3_cln, y = df_ms_cln,
    x_id_col = "ptid", y_id_col = "subject_id",
    x_date_col = "form_date", y_date_col = "exam_date",
    x_intvl_less = 120, x_intvl_more = 120,
    keep_y_id = FALSE
  )
# glimpse(df_u3_ms)
```

# Filter for Study Criteria

Get NLs (26) or MCIs (1, 2, 27, 28, 31, 34).
```{r}
target_dx <- as.integer(c(26, 1, 2, 27, 28, 31, 34))

df_u3_ms_trg <- df_u3_ms %>% 
  filter(uds_dx %in% target_dx)

df_u3_ms_trg %>% 
  group_by(uds_dx) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n))
```

Get >= 65 years old.
```{r}
df_u3_ms_trg <- df_u3_ms_trg %>%
  filter(age_exact >= 65.00)
# min(df_u3_ms_trg$age_exact)
```

Get white (1) or black (2) race.
```{r}
target_race <- as.integer(c(1, 2)) # 1 Wht, 2 Blk

df_u3_ms_trg <- df_u3_ms_trg %>% 
  filter(race_value %in% target_race)
```

Get those with a study partner.
```{r}
df_u3_ms_trg <- df_u3_ms_trg %>% 
  filter(!is.na(so_fname))
```

**DO NOT APPLY** - Get those for whom feedback has been given.
```{r}
df_u3_ms_trg_fb <- df_u3_ms_trg # %>%
  # filter(fb_complete == 1L)
```

Get only latest visit.
```{r}
df_u3_ms_trg_fb_dedup <- df_u3_ms_trg_fb %>% 
  calculate_visit_num(ptid, form_date) %>% 
  arrange(ptid, desc(form_date)) %>% 
  group_by(ptid) %>% 
  mutate(max_visit_num = max(visit_num)) %>% 
  filter(visit_num == max_visit_num) %>% 
  select(-max_visit_num)
```

**DO NOT APPLY** - Get only visits with last 12 months.
```{r}
# df_u3_ms_trg_fb_dedup <- df_u3_ms_trg_fb_dedup %>% 
#   filter(form_date >= (today() - months(12)))
```


```{r}
# df_u3_ms_trg_fb_dedup %>% 
#   group_by(uds_dx) %>% 
#   summarize(n = n())

df_u3_ms_trg_fb_dedup %>%
  mutate(dx_cat = case_when(
    is.na(uds_dx) ~ NA_character_,
    uds_dx == 26L ~ "NL",
    TRUE ~ "MCI"
  )) %>%
  group_by(dx_cat) %>%
  summarize(n = n())
```

```{r}
df_u3_ms_trg_fb_dedup %>% 
  select(ptid, form_date, uds_dx)
```


# Filter Out Sherry's Existing List

Load Sherry's spreadsheet.
```{r}
df_sherry <- readxl::read_excel("./MCI-DEM participants-List 1_2-01-2019.xlsx")
```

Get IDs in Sherry's spreadsheet.
```{r}
ids_sherry <- df_sherry %>% pull(`Subject ID`)
ids_sherry
```

Filter out Sherry spreadsheet IDs.
```{r}
df_u3_ms_trg_fb_dedup_nots <- df_u3_ms_trg_fb_dedup %>% 
  filter(!(ptid %in% ids_sherry))
```

# Write to CSV

```{r}
readr::write_csv(df_u3_ms_trg_fb_dedup_nots, 
                 "New MCI-DEM participants-List 2_2019-02-04.csv", 
                 na = "")
```



```{r echo = FALSE}
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
